Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-15 thesis/thesis.tex
thesis: Review Conclusions and Future Work

\section{Comparing and Validating}

@@

As shown by the obtained results, we can say that in general our model works fine identifying and characterizing open clusters.
So we have succedded building a model non-parameterized non-supervised for open cluster characterization.
However, some improvements should be done in order to improve its accuracy and precision.

@@

Another key point in our model is the initializer kernel.
This kernel prepares data before passing it to the ANN and the results may vary significantly depending on this kernel.
For example, simply varying the kernel seed can make a huge difference on the result.

@@

With all of this points in mind, we can affirm that this model could be really considered as an alternative model for open cluster characterization and thus,
it could even be incloud as part of the Virtual Observatory toolset.

@@

The first aim after finishing this work is testing the model with a wider range of clusters.
In general we could think of applying it to the whole VizieR catalogue.
That way we could have a better idea about the current limits of our model and we could make adjustments to improve it.
We could determine with better accuracy the topologies that our model works well with, and which ones out model does not resolve properly.
Or even, we could stablish different sets of hyperparameters regarding the topology of the cluster.

@@

Another possible change in our model would be using DBSCAN instead of KMeans as our initial clustering algorithm.
Maybe this algorithm gives us a better starting point for the DEC model.

At last, we have used during this work the Gaia DR2 database, but recently the DR3 dataset has been released.
So it is evident the interest on testing our model with this new data.

>>>>

\section{Comparing and Validating}
\label{sec:comparing_and_validating}

@@

From the results shown in Chapter \ref{sec:comparing_and_validating},
we can say that, in general, our model works fine identifying and characterizing open clusters.
So we have succedded building a model non-parameterized and non-supervised for open cluster characterization.
However, some improvements should be done in order to improve its accuracy and precision.

@@

Another key point in our model is the initializer kernel.
This kernel prepares data before passing it to the ANN
and the results may vary significantly depending on this kernel.
For example, simply varying the kernel seed can make a huge difference on the result.
This is something to avoid, so an improvement to solve this issue is necessary in order
to have a reliable model which does not depend on the dataset order.

@@

With all of these points in mind and once the mentioned issues have been solved,
we can assert this model could be considered as a valid model for open cluster characterization.
And thus, it could even be included as part of the Virtual Observatory toolset.

@@

The first aim after finishing this work is testing the model with a wider range of clusters.
In general we could think of applying it to the whole VizieR catalogue.
That way we could have a better idea about the current limits of our model and we could make adjustments to improve it.
We could determine with better accuracy the topologies that our model works well with,
and which ones the model does not resolve properly.
Even, we could stablish different sets of hyperparameters regarding the topology of the cluster.

@@

Another possible change in our model would be using DBSCAN instead of KMeans as our initial clustering algorithm.
Maybe this algorithm gives us a better starting point for the DEC model which could improve the results.

At last, we have used the Gaia DR2 database as our data source for this work,
but recently the DR3 dataset has been released.
So it is evident the interest on testing our model with this new data.
